Manuscript

### 2024-05-20 Sections/htw_full.qmd
updated full manuscript version; tweak website themes; might not work due to date format in gfm

---
title: HTW Full w/Code
author:
- name: Thomas E. Gorman
  affiliations: 
   - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Robert L. Goldstone
  affiliation: Department of Psychological and Brain Sciences, Indiana University-Bloomington
  url: https://pc.cogs.indiana.edu/
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
date: last-modified
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
repo-actions: false
execute: 
  warning: false
  eval: true
---
_______________________________________________________________________________
{{< fa file-lines >}} [Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \

@@

## Methods

>>>>

---
title: Impact of Training Variability on Visuomotor Function Learning and Extrapolation
author:
- name: Thomas E. Gorman
  affiliations: 
   - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Robert L. Goldstone
  affiliation: Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://pc.cogs.indiana.edu/
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
date: last-modified
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
repo-actions: false
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: htw_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: htw_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "htw.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "htw.docx"
    toc: true
prefer-html: true
---

::: {.content-visible when-format="html"}
_______________________________________________________________________________
{{< fa file-lines >}} [Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \

@@

### Methods

### 2024-05-20 Simulations/DeLosh97_Sim.qmd
updated full manuscript version; tweak website themes; might not work due to date format in gfm

```{r}
#https://nrennie.rbind.io/blog/2022-06-06-creating-flowcharts-with-ggplot2/
inNodes <- seq(1,6,1) %>% as.integer()
outNodes <- seq(300,1000,50)%>% as.integer()
stim <- "Stim"
resp <- "Response"
inFlow <- tibble(expand.grid(from=stim,to=inNodes)) %>% mutate_all(as.character)
outFlow <- tibble(expand.grid(from=outNodes,to=resp)) %>% mutate_all(as.character)

@@

```{r}
#| code-fold: show
#| code-summary: "Toggle Code"
alm.response <- function(input = 1, c, input.layer, output.layer,weight.mat) {
  input.activation <- exp(-c * (input.layer - input)^2) / sum(exp(-c * (input.layer - input)^2))
  output.activation <- weight.mat %*% input.activation
  output.probability <- output.activation / sum(output.activation)
  mean.response <- sum(output.layer * output.probability)
  list(mean.response = mean.response, input.activation = input.activation, output.activation = output.activation)
}
```

>>>>

```{r}
#https://nrennie.rbind.io/blog/2022-06-06-creating-flowcharts-with-ggplot2/
inNodes <- seq(1,6,1) %>% as.integer()
outNodes <- seq(300,1000,50)%>% as.integer()

stim <- "Stim"
resp <- "Response"
inFlow <- tibble(expand.grid(from=stim,to=inNodes)) %>% mutate_all(as.character)
outFlow <- tibble(expand.grid(from=outNodes,to=resp)) %>% mutate_all(as.character)

@@

```{r}
##| code-fold: show
#| code-summary: "Toggle Code"
alm.response <- function(input = 1, c, input.layer, output.layer,weight.mat) {
  input.activation <- exp(-c * (input.layer - input)^2) / sum(exp(-c * (input.layer - input)^2))
  output.activation <- weight.mat %*% input.activation
  output.probability <- output.activation / sum(output.activation)
  mean.response <- sum(output.layer * output.probability)
  list(mean.response = mean.response, input.activation = input.activation, output.activation = output.activation)
}
```

### 2024-05-20 paper.qmd
update htw_full to match dissertation version
updated full manuscript version; tweak website themes; might not work due to date format in gfm

---
title: Manuscript
toc: false
page-layout: full
---

@@

@@

  <!-- <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
  </a>
   -->
  <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscripty PDF
  </a>

>>>>

---
title: Manuscript
subtitle: Impact of Training Variability on Visuomotor Function Learning and Extrapolation
toc: false
page-layout: full
---

{{< iconify <icon> >}}

@@

      <a class="btn btn-success btn-sm mb-1" href="/Sections/htw_full.html" target="_blank">
  <iconify-icon inline="" icon="fa6-solid:arrow-up-right-from-square"></iconify-icon> &ensp;HTML <small>(code included)</small>
  </a>

@@

  <!-- <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
  </a>
   -->
  <!-- <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscripty PDF
  </a>  -->

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/Manuscript/output/htw_manuscript.docx">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;docx <small>(download)</small>
  </a>
